### 2018-02-10 results.Rnw
fixes #1
fixes #6, fixes #3

\begin{figure}[!h]
	\includegraphics[width=1\textwidth]{fig/fig-3.pdf}
	\caption{{\bf Experiment quality control.}
			Tile plot representing the fraction of time spent moving as a colour intensity.
			Each individual is represented by a row and time, on the x axis, is binned in 30 minute.}
	\label{fig:fig-3}
\end{figure}

@@

<<cache=TRUE>>=
# we also show a subset of this figure in supplementary materials
figS1A <- ggetho(dt, aes(z = moving), multiplot = 2) +
            # bars n the z axis could 
            #  one could also use stat_tile_etho
            stat_bar_tile_etho() + 
            # divide plot by individual
            facet_wrap( ~ label, ncol = 4) +
            # rename the y axis
            scale_y_discrete(name="Day")
@
<<cache=TRUE, echo=FALSE>>=
fig_4_picked_labels = paste(c(5,10,33,39, 13,17,22,51), rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4), sep=".")

fig4A <- ggetho(dt[xmv(label) %in% fig_4_picked_labels],
						 aes(z = moving), multiplot = 2) +
	stat_bar_tile_etho() + 
	facet_wrap( ~ label, ncol = 4) +
	scale_y_discrete(name="Day")
@

@@

<<cache=TRUE, echo=FALSE>>=
fig4B <- ggperio(per_dt[xmv(label) %in% fig_4_picked_labels],
aes(y = power, peak=peak)) + 
# periododogram drawn as a line
geom_line() +
# the significance line in red
geom_line(aes(y = signif_threshold), colour="red") + 
# point and text at the peak
geom_peak() + 
# divide plot by individual
facet_wrap( ~ label, ncol = 4) 
@

\begin{figure}[!h]
	\includegraphics[width=1\textwidth]{fig/fig-4.pdf}
	\caption{{\bf Visualisation of the periodicity in activity of eight representative animals.}
		A: Double plotted actograms showing activity over the experiment. Transition to LL happens at day 0.
		B: $\chi{}^2$ periodograms over the LL part of the experiment matching the animals in A.
		Titles on top of each facet refer to the label allocated to each individual.
		A version of this figure with all animals is available \nameref{S1-Fig}.
	}
	\label{fig:fig-4}
\end{figure}

@@

\begin{figure}[!h]
	\includegraphics[width=1\textwidth]{fig/fig-5.pdf}
	\caption{{\bf Population statistics on circadian phenotype.}
			A: Average periodograms. 
			      The aggregated relative power of the periodogram of all animals.
			      The lines shows and the shaded areas show population means and their 95\% bootstrap confidence interval, respectively.
			B: Peak periodicity power and average.
			      Values of the peak period for animals with a significant peak.
			      Individual animals are shown by dots whose size represent power of the peak period.
			      The error bars are 95\% bootstrap confidence interval on the population mean.
			C: Frequencies of rhythmic animals.
			      Number of rhythmic animals (\emph{i.e.} with a significant peak) in each genotypes.
			      Dark and clear fillings indicate rhythmic and arhythmic animals, respectively.
			      }
	\label{fig:fig-5}
\end{figure}

@@

legend <- fig3A + theme(axis.title=element_blank(),
                        axis.text.x=element_blank(),
                        axis.ticks=element_blank(),
                        axis.line = element_blank(),
                        #axis.ticks.y=element_blank(),
                        panel.border = element_blank(),
                        #legend.text = "moving",
                        legend.position="left") + 
                  coord_cartesian(xlim=-days(c(10, 9))) + scale_y_discrete(position = "right")

fig3 <- cowplot::plot_grid(
                          legend,
                          fig3A +  my_theme,
                          fig3B +  my_theme,
                          nrow=1,
                          labels=c("A", "", "B"),
                          rel_widths = c(1, 2, 2),
                          label_size = 32,
                          axis="b",
                          align="h",
                          hjust=0, vjust=1.01
                          )
pdf("../fig/fig-3.pdf",w=12,h=12)
print(fig3)
tmp  <- dev.off()

@@

fig4 <- cowplot::plot_grid(
				fig4A,
				fig4B,
				nrow=1,
				labels=c("A", "B"),
				align="v",
				axis="b",
				label_size = 32,
				hjust=0, vjust=1.01
)

pdf("../fig/fig-4.pdf",w=12,h=4)
print(fig4)
tmp  <- dev.off()

@@

fig5 <- cowplot::plot_grid(fig5A + theme(legend.position="none"),
                           fig5B + theme(legend.position="bottom"),
                           fig5C + theme(legend.position="none"),
                           nrow=1,
                           label_size = 32,
                           align = "hv",
                           axis="b",
                           labels=c( "A", "B", "C"),
                           hjust=0, vjust=1.01
                           #?cowplot::plot_grid
                           )
pdf("../fig/fig-5.pdf",w=12,h=6)
print(fig5)
tmp <- dev.off()
@

>>>>

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-3.pdf}
	\caption{{\bf Experiment quality control.}
			Tile plot representing the fraction of time spent moving as a colour intensity.
			Each individual is represented by a row and time, on the x axis, is binned in 30 minute.}
	\label{fig:fig-3}
\end{figure}

@@

<<cache=TRUE, warning=FALSE>>=
# we also show a subset of this figure in supplementary materials
figS1A <- ggetho(dt, aes(z = moving), multiplot = 2) +
            # bars n the z axis could 
            #  one could also use stat_tile_etho
            stat_bar_tile_etho() + 
            # divide plot by individual
            facet_wrap( ~ label, ncol = 4) +
            # rename the y axis
            scale_y_discrete(name="Day")
@

<<cache=TRUE, echo=FALSE>>=
#fig_4_picked_labels = paste(c(5,10,33,39, 13,17,22,51), rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4), sep=".")
helper_dt_picked_labs <- data.table(num = c(5,10,33,39, 13,17,22,51),
                                    genotype =  rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4))
helper_dt_picked_labs[,label := interaction(num, genotype)]

  # add a bg that depends on labels
bg_layer =   geom_rect(data=helper_dt_picked_labs, aes(fill=genotype),
            xmin = -Inf,xmax = Inf,
            ymin = -Inf,ymax = Inf,
            alpha = 0.3, inherit.aes = F)

fig_4_picked_labels = helper_dt_picked_labs[,label]

fig4A <- ggetho(dt[xmv(label) %in% fig_4_picked_labels],
						 aes(z = moving), multiplot = 2) +
  bg_layer+
	stat_bar_tile_etho() + 
	facet_wrap( ~ label, ncol = 4) +
	scale_y_discrete(name="Day") +
  theme(strip.text= element_text(size = 11))

ylabs <- ggplot_build(fig4A)$layout$panel_ranges[[1]]$y.labels
fig4A <- fig4A + scale_y_discrete(name="Day",
                                  limits = ifelse(1:length(ylabs) %%2, ylabs, ""))
@

@@

<<cache=TRUE, echo=FALSE, warning=FALSE>>=
fig4B <- ggperio(per_dt[xmv(label) %in% fig_4_picked_labels],
                      aes(y = power, peak=peak)) + 
            # periododogram drawn as a line
            geom_line() +
            bg_layer+
            # the significance line in red
            geom_line(aes(y = signif_threshold), colour="red") + 
            # point and text at the peak
            geom_peak() + 
            # divide plot by individual
            facet_wrap( ~ label, ncol = 4) + 
            scale_y_continuous(name="Power") +
            theme(strip.text= element_text(size = 11))

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-4.pdf}
	\caption{{\bf Visualisation of the periodicity in activity of eight representative animals.}
		A: Double plotted actograms showing activity over the experiment. Transition to LL happens at day 0.
		B: $\chi{}^2$ periodograms over the LL part of the experiment matching the animals in A.
		The blue annotation represents the first peak (if present) above the significance threshold (red line).
		Titles on top of each facet refer to the label allocated to each individual.
		A version of this figure with all animals is available \nameref{S1-Fig}.
	}
	\label{fig:fig-4}
\end{figure}

@@

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-5.pdf}
	\caption{{\bf Population statistics on circadian phenotype.}
			A: Average periodograms. 
			      The aggregated relative power of the periodogram of all animals.
			      The lines shows and the shaded areas show population means and their 95\% bootstrap confidence interval, respectively.
			B: Peak periodicity power and average.
			      Values of the peak period for animals with a significant peak.
			      Individual animals are shown by dots whose size represent power of the peak period.
			      The error bars are 95\% bootstrap confidence interval on the population mean.
			C: Frequencies of rhythmic animals.
			      Number of rhythmic animals (\emph{i.e.} with a significant peak) in each genotypes.
			      Dark and clear fillings indicate rhythmic and arhythmic animals, respectively.
			      }
	\label{fig:fig-5}
\end{figure}

@@

legend <- fig3A + theme(axis.title=element_blank(),
                        axis.text.x=element_blank(),
                        axis.ticks=element_blank(),
                        axis.line = element_blank(),
                        #axis.ticks.y=element_blank(),
                        panel.border = element_blank(),
                        #legend.text = "moving",
                        legend.position="none") + 
                  coord_cartesian(xlim=-days(c(10, 9))) + scale_y_discrete(position = "right")

fig3 <- cowplot::plot_grid(
                          legend,
                          fig3A +  my_theme,
                          fig3B +  my_theme,
                          nrow=1,
                          labels=c("A", "", "B"),
                          rel_widths = c(1, 2, 2),
                          label_size = 32,
                          axis="b",
                          align="h",
                          hjust=0, vjust=1.01
                          )
fill_legend <- 
  cowplot::plot_grid(NULL,
    cowplot::get_legend(
        fig3A + theme(legend.position = "bottom", legend.direction = "horizontal") + scale_fill_continuous(labels = scales::percent, name="Moving ", breaks=c(0,.5,1))
        ), NULL
    )
#?theme

fig3_final <- cowplot::plot_grid(fig3, fill_legend,nrow = 2, rel_heights = c(15,1))

pdf("../fig/fig-3.pdf",w=12,h=12)
print(fig3_final)
tmp  <- dev.off()

@@

fig4 <- cowplot::plot_grid(
				fig4A + theme(legend.position = "none"),
				fig4B+ theme(legend.position = "none"),
				nrow=1,
				labels=c("A", "B"),
				align="v",
				axis="b",
				label_size = 32,
				hjust=0, vjust=1.01
)

fill_legend <- 
  cowplot::plot_grid(NULL,
    cowplot::get_legend(
        fig4A + theme(legend.position = "bottom", legend.direction = "horizontal") + scale_fill_discrete(name="Genotype "))
        )
#?theme

fig4_final <- cowplot::plot_grid(fig4, fill_legend,nrow = 2, rel_heights = c(15,1))
pdf("../fig/fig-4.pdf",w=12,h=4)
print(fig4_final)
tmp  <- dev.off()

@@

fig5 <- cowplot::plot_grid(fig5A + theme(legend.position="none"),
                           fig5B + theme(legend.position="none") + scale_x_discrete(name="Genotype"),
                           fig5C + theme(legend.position="none") + scale_y_continuous(name="Number") +
                             scale_x_discrete(name="Genotype"),
                           nrow=1,
                           label_size = 32,
                           align = "hv",
                           axis="b",
                           labels=c( "A", "B", "C"),
                           hjust=0, vjust=1.01
                           #?cowplot::plot_grid
                           )

dummy <- ggplot(summary_dt, aes(is_rhythmic, first_peak_period, size= first_peak_power, fill= genotype, colour=genotype)) + 
    geom_bar(aes(x=genotype, alpha= ifelse(is_rhythmic, "Rhythmic", "Arhythmic"), fill=genotype), inherit.aes = F) + 
  geom_jitter(aes(is_rhythmic, first_peak_period, size=first_peak_power), inherit.aes = F) +
   scale_fill_discrete(name="Genotype")+scale_size(name= "Peak power") +  scale_alpha_discrete(name= "") +
  theme(legend.position = "bottom")  + 
  guides(fill = guide_legend(order=1),
         size = guide_legend(order=2),
         alpha = guide_legend(order=3))

legend <- plot_grid(NULL, get_legend(dummy), NULL, nrow=1)

fig5_final <- cowplot::plot_grid(fig5, legend, nrow = 2, rel_heights = c(15,1))
pdf("../fig/fig-5.pdf",w=12,h=6)
print(fig5_final)
tmp <- dev.off()
@
